---
title: "Statistical Inference Course Project"
author: "monade"
date: "12 Sep 2015"
output: pdf_document
---

### Overview
This investigates a simulation taken from an exponential distribution and interferes some properties from the simulated data. These properties are compared with the theoretical values.

### Simulations

Draw a sample taken from averages of an exponential distribution
```{r}
set.seed( 37 )
lambda <- 0.2
N      <- 1000
D      <- 40
sample <- replicate( N, mean( rexp( D, lambda)))
```

Evaluate sample mean/variance and theoretical mean/variance
```{r}
m    <- mean( sample )
var  <- sum( (sample-m)^2)/(N-1) 
stddev <- sqrt( var )
tm   <- 1/lambda
tvar <- (1/lambda)^2/D
tstddev <- sqrt(tvar)
```

Plot histogram
```{r}
hist( sample, freq=F, ylim=c(0,0.8), breaks=20,
      main="Histogram with sample and theo means and standard deviation")
lines( seq(3, 8, 0.1), dnorm(seq(3, 8, 0.1), tm, tvar), col="Green")
abline(v=c(m-stddev, m, m+stddev), col="Red")
text(7,0.5,"sample mean+-stddev", col="Red")
abline(v=c(tm-tstddev, tm, tm+tstddev), col="Blue")
text(7,0.45,"theo mean+-?stddev", col="Blue")
text(7, 0.4, "normal distribution", col="Green")
```

Sample mean and variance
```{r}
c( m, var)
```

Theoretical mean and variance
```{r}
c( tm, tvar)
```

Relative differences
```{r}
c((m-tm)/tm,(var-tvar)/tvar)
```

The mean of the exponential distributions resembles the theoretical limit distribution, which is a normal distribution.
