---
title: "Statistical Inference Course Project Tooth Growth"
author: "monade"
date: "26 Sep 2015"
output: pdf_document
---

Load Tooth Growth data
```{r, warning=FALSE, message=F}
library(dplyr)
data( ToothGrowth )
tg <- ToothGrowth
```

Summarize data by groups
```{r}
tg_group <- group_by( tg, supp, dose)
len_means <- summarize( tg_group, mean = mean(len))
len_means
```

Plot of Tooth Growth length on Vitamin C delivery by Orange Juice and Ascorbic Acid
```{r}
len_vc <- len_means$mean[1:3]
len_oj <- len_means$mean[4:6]
m <- matrix(c(len_vc, len_oj), ncol=3, byrow=TRUE)
barplot(m, beside=TRUE, names=len_means$dose[1:3], main="Tooth Growth on Vitamin C delivery by Orange Juice and Ascorbic Acid")
```

The mean of the tooth growth are higher for doses 0.5 and 1 with Orange Juice delivery

One sided t tests for each dose delivery
```{r}
test_length_by_dose = function( d )
{
  vc <- filter(tg_group, supp=="VC", dose==d)$len
  oj <- filter(tg_group, supp=="OJ", dose==d)$len
  t.test(oj, vc, alternative="greater")
}

test_length_by_dose( 0.5 )
test_length_by_dose( 1 )
test_length_by_dose( 2 )
```

The p values for the doses 0.5 an 1 are sufficient small for an indication of a greater tooth growth length by delivery with Orange Juice. For doses 2 there is no indication.